---
title: 'matricks: Useful Tricks for Matrix Manipulation'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
`matricks` package in **0.8.2** version has been released on CRAN! In this post I will present you, what are advantagese of using `matricks` and how you can use it.

### Creating matrices
The main function the package started with is `m`. It's a smart shortcut for creating matrices, especially usefull if you want to define a matrix by enumerating all the elements row-by-row. Typically, if you want to create a matrix in R, you can do it using `base` function called `matrix`.

```{r base.matrix}
matrix(c(3 ,4, 7,
         5, 8, 0,
         9, 2, 1), nrow = 3, byrow = TRUE)
```
Although it's a very simple opeartion, the funtion call doesn't look tidy. Alternaively, we can use `tibble` with its `frame_matrix` function, defining column names with formulae first.

```{r tibble}
library(tibble)
frame_matrix(~ c1, ~ c2, ~ c3,
                3,    4,    7,
                5,    8,    0,
                9,    2,    1)
```
However, it's still not a such powerfull tool as `matricks::m` function is. Let's see an example.

```{r matricks.m}
library(matricks)
m(3 ,4, 7|
  5, 8, 0|
  9, 2, 1)
```
As simple as that! We join following rows using `|` operator.   `m` function is very flexible and offers you much more than before mentioned ones. 
```{r matricks.vectors}
m(1:3 | 4, 6, 7 | 2, 1, 4)
```

And here and example with bindig multiple matrices together:
```{r matricks.binding}
dmat   <- diag(1, 3, 3)
dmat3  <- antidiag(1, 3, 3) * 3
m(dmat , dmat3|
  dmat3, dmat)
```
By the way, `antidiag` function can be found in the `matricks` package too.

### Settinh & accessing values
These code 
```{r setting.matrix}
mat <- matrix(0, 3, 3)
mat[1, 2] <- 0.3
mat[2, 3] <- 7
mat[3, 1] <- 13
mat[2, 2] <- 0.5
mat
```
can be replaced with:
```{r matricks.sv}
mat <- matrix(0, 3, 3)
mat <- set_values(mat,
                  c(1, 2) ~ 0.3,
                  c(2, 3) ~ 7,
                  c(3, 1) ~ 13,
                  c(2, 2) ~ 0.5)
mat
```

At 

```{r matricks.at}
mat <- matrix(0, 3, 3)
at(mat, c(2, 3)) <- 75
mat
```


### Plotting matrix
`matrix` objects haven't had good automatized plotting function until now. Let's create an 

```{r matricks.runifm}
rmat <- runifm(3, 3)
print(rmat)
plot(rmat)
```

```{r matricks.rboolm}
set.seed(7)
rmat <- rboolm(3, 3)
print(rmat)
plot(rmat)
```
